|

### 2021-08-06 appendix/appendix.Rmd
add lower bound book appendix

\begin{proof}
Note that the $\underline{x}_m^g = 2p + \underline{x}_o^g$. As the political disagreement is higher than zero, $\underline{x}_m^g = - 2p + \underline{x}_o^g < \underline{x}_o^g$. Moreover, note that $\underline{x}_m^g - \underline{x}_o^g = -2p$.
\end{proof}

This characterizes the offer that the mayor will make to win the support of the council. Now, let the number of government politicians be equal to $\eta_g$, and the ex-ante probability of electing a councilor aligned with the government equal to $\gamma \in (0,1)$. We define the cost to govern $C_g(N)$ as XXXX:

\[
C_g(N) = \dfrac{N}{2}(\underline{t} + \underline{x}_o^g) + \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\left( \underline{x}_m^g - \underline{x}_o^g \right)
\]

@@

\[
\begin{aligned}
\max_{r, g} \quad & u(r) + B_M\pi(g)\\
\textrm{s.t.} \quad & r + g + C_g(N) \leq R
\end{aligned}
\]

@@

\[
\max_{g} \{ u(R - g - C_g(N)) + B_M\pi(g) \}
\]

@@

\[
u'(R - g - C_g(N)) = B_M\pi'(g)
\]

This is sufficient for the equilibrium, as the second order condition reassures the concavity of the mayor's expected utility: $u''(R - g^* - C_g(N)) + B_M\pi''(g^*) < 0$.

@@

The mayor's expected utility
\end{proof}

>>>>

\begin{proof}
Note that the $\underline{x}_m^g = 2p + \underline{x}_o^g$. As the political disagreement is higher than zero, $\underline{x}_m^g = - 2p + \underline{x}_m^o < \underline{x}_m^g$. Moreover, note that $\underline{x}_m^g - \underline{x}_m^o = -2p$.
\end{proof}

This characterizes the offer that the mayor will make to win the support of the council. Now, let the number of government politicians be equal to $\eta_g$, and the ex-ante probability of electing a councilor aligned with the government equal to $\gamma \in (0,1)$. We define the cost to govern $C_G(N)$ as XXXX:

\[
C_G(N) = \dfrac{N}{2}(\underline{t} + \underline{x}_o^g) + \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\left( \underline{x}_m^g - \underline{x}_m^o \right)
\]

@@

\[
\begin{aligned}
\max_{r, g} \quad & u(r) + B_M\pi(g)\\
\textrm{s.t.} \quad & r + g + C_G(N) \leq R
\end{aligned}
\]

@@

\[
\max_{g} \{ u(R - g - C_G(N)) + B_M\pi(g) \}
\]

@@

\[
u'(R - g - C_G(N)) = B_M\pi'(g)
\]

This is sufficient for the equilibrium, as the second order condition reassures the concavity of the mayor's expected utility: $u''(R - g^* - C_G(N)) + B_M\pi''(g^*) < 0$.

@@

The mayor's expected utility satisfy the increasing differences in $g$ and $N$ when, for $g > g'$ and $N+1>N$, we have:

\[
\mathbb{E}\text{U}(g, N+1) - \mathbb{E}\text{U}(g', N+1) \geq \mathbb{E}\text{U}(g, N) - \mathbb{E}\text{U}(g', N)
\]

And after substituting, we have:

\[
u(R - g - C_G(N+1)) + B_M\pi(g) - u(R - g' - C_G(N+1)) - B_M\pi(g')
\\
\geq 
\\
u(R - g - C_G(N)) + B_M\pi(g) - u(R - g' - C_G(N)) - B_M\pi(g')
\]

Which is equal to:

\[
u(R - g - C_G(N+1)) - u(R - g' - C_G(N+1)) \geq 
u(R - g - C_G(N)) - u(R - g' - C_G(N))
\]

Multiplying both sides by $\dfrac{1}{g - g'}$ and taking the limit when $g \rightarrow g'$, we have:

\[
u'(R - g - C_G(N+1)) \geq 
u'(R - g - C_G(N))
\]

This is true when the cost of govern with a council size of $N+1$ is lower than the cost of govern when the council size has $N$ councilors:

\[
C_G(N+1) \leq C_G(N)
\]

Therefore, to satisfy increasing differences in XXXX,

\end{proof}

This gives us our first empirical hypothesis to test: if the cost of govern decreases when the legislature increases, then the public goods provision increase when the legislature size increase. Moreover, the rents also increase with the legislature size.

\begin{proposition}

There exists a probability of electing a councilor aligned with the government $\gamma^*$ such that, for all $\gamma > \gamma^*$, the cost of govern decreases as $N$ increases, i.e. $C_G(N+1) \leq C_G(N)$.

\end{proposition}

\begin{proof}

If the proposition is correct, then $C_G(N-1) - C_G(N+1) \geq 0$. Note that the differences for the partial binomial sums are increasing in $\gamma$ [@worsch1994lower]. However, if we open up the difference:

\end{proof}
